---
title: "Some plots about NYC restaurants"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

I like to eat! Let's investigate some restaurants in the Big Apple.

Chart A shows NYC Department of Health scores for Korean restaurants in Manhattan by year of inspection. Chart B depicts American restaurants in NYC, separated by borough. Chart C shows DOH scores for Chinese restaurants by borough.

Whew! All those charts are making me hungry. Time for a snack!

```{r, include = FALSE}
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(plotly)
library(flexdashboard)
```

Column {data-width = 650}
-----------------------------------------------------------------------

### Chart A
```{r plot_a}
nyrest_a = read_csv("./data/DOHMH_New_York_City_Restaurant_Inspection_Results.csv.gz") %>% 
  janitor::clean_names() %>% 
  filter(!is.na(grade),
         boro == "MANHATTAN",
         cuisine_description == "Korean") 

nyrest_a %>% 
  mutate(text_label = str_c("Type of warning: ", critical_flag, "\nScore: ", score),
         year = lubridate::year(inspection_date)) %>% 
  plot_ly(x = ~year, y = ~score, type = "scatter", mode = "markers",
          alpha = 0.5,
          color = ~critical_flag,
          text = ~text_label)
```


Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r plot_b}
nyrest_b = read_csv("./data/DOHMH_New_York_City_Restaurant_Inspection_Results.csv.gz") %>% 
  janitor::clean_names() %>% 
  filter(cuisine_description == "American")

nyrest_b %>% 
  count(boro) %>% 
  mutate(boro = fct_reorder(boro, n)) %>% 
  plot_ly(x = ~boro, y = ~n, color = ~boro, type = "bar")
```

### Chart C

```{r plot_c}
nyrest_c = read_csv("./data/DOHMH_New_York_City_Restaurant_Inspection_Results.csv.gz") %>% 
  janitor::clean_names() %>% 
  filter(cuisine_description == "Chinese")

nyrest_c %>% 
  mutate(boro = fct_reorder(boro, score)) %>% 
  plot_ly(y = ~score, color = ~boro, type = "box", colors = "Set2")
```

